Computer Science House Constitution

### 2022-02-15 constitution.tex
constitution: review feedback

\asubsection{Waiving of Qualifications}
\begin{enumerate}
  \item The following Qualifications may be waived as decided by a Two-Thirds Immediate Vote as described in \ref{Two-Thirds} and \ref{Immediate Vote}:
    \begin{enumerate}
      \item Candidates must reside on floor during the term of office.
      \item Candidates must have at least one full semester of House membership as an Active Member.
      \item Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
    \end{enumerate}
  \item Each vote to waive a Qualification must only apply to a single Qualification and a single Selection.
  \item The chair of the vote shall state what qualification waiver is being voted upon, what Selection the waiver will apply to, and any nominated candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
\end{enumerate}

>>>>

\asubsection{Waiving of Qualifications}
\begin{enumerate}
  \item House may choose to waive the following subset of the Qualifications for Executive Board positions (defined under \ref{Qualifications}) for all Candidates:
    \begin{enumerate}
      \item Candidates must reside on floor during the term of office.
      \item Candidates must have at least one full semester of House membership as an Active Member.
      \item Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
    \end{enumerate}
  \item When a waiver is proposed, the Chair of the Vote shall state which Executive Board position and Qualification is being voted upon, and any nominated Candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
  \item A Two-Thirds Immediate Vote, as defined in \ref{Two-Thirds} and \ref{Immediate Vote}, is then taken to determine whether the proposed waiver shall take effect.
  \item Each vote to waive a Qualification must only apply to a single Qualification for a single Executive Board position.
  \item Waivers always apply to all Candidates for the Executive Board position.
\end{enumerate}
